### 2014-04-16 doc/uist14/relatedwork.tex
remove space before the reference in related work

Other targeting systems use IR with handheld pointers ~\cite{swindells_that_2002} and as well as wearable devices such as rings and Bluetooth audio earpieces ~\cite{merrill_augmenting_2007} to connect to smart devices. Our system tackles an unresolved issue of such IR-based approaches-- navigating an area dense with potential targets.

>>>>

Other targeting systems use IR with handheld pointers~\cite{swindells_that_2002} and as well as wearable devices such as rings and Bluetooth audio earpieces~\cite{merrill_augmenting_2007} to connect to smart devices. Our system tackles an unresolved issue of such IR-based approaches -- navigating an area dense with potential targets.
